Data Provenance for Concurrent Program Debugging and Analysis in Production Systems

### 2013-11-11 paper.tex
committing changes to the eval that add a table and our new eval criteria

{\bf TODO: Table showing the bugs we looked at, vital stats, comparison to origin tracking}

@@

\begin{table}
\begin{tabular}{l|l|ccc}
{\bf App} & {\bf Type} & {\bf Eff.?} & {\bf Triv.?} & {\bf Usef.?} \\ \hline
mysql   & Atom.  &Yes  &No & Yes    \\
pbzip2  & Order  &Yes  &No & Yes    \\
httrack & Order  &Yes  &No & Yes    \\
jdk-sb  & Atom.  &Yes  &No & Yes    \\
apache1 & Atom.  &Yes  &No & Yes    \\ 
apache2 & Atom.  &Yes  &No & Maybe  \\
\end{tabular}
\caption{{\bf Evaluation of debugging with last writer slices.} We describe each bug and summarize the debugging benefit of last writer slices using the evaluation criteria from ~\cite{badapples}.}
\end{table}

>>>>

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{l|ll|l|ccc|c}
{\bf App} & {\bf Ver. \#} & {\bf Bug \#} &{\bf Type} & {\bf Eff.?} & {\bf Triv.?} & {\bf Usef.?} & {\bf O.T.?}\\ \hline
mysql  &  4.0.12 &  791     & Atom.  &Yes  &No    & Yes   & No  \\%All values usable
pbzip2 &  0.9.4  &  N/A     & Order  &Yes  &No    & Yes   & Yes \\
httrack& 3.43.9  &  N/A     & Order  &Yes  &No    & Yes   & No  \\%Used w/o origin - no help
jdk1.4 &  1.70   &          & Atom.  &Yes  &No    & Yes   & No  \\%All values usable
apache1&  2.0.48 &  21285   & Atom.  &Yes  &No    & Yes   & No  \\%All values usable
apache2&  2.2.9  &  45605   & Atom.  &Yes  &No    & Maybe & ??  \\
\end{tabular}
\caption{{\bf Debugging with last writer slices.} We describe each bug and summarize the debugging benefit of last writer slices using the evaluation criteria from ~\cite{badapples}.  }
\normalsize
\end{table}
